---
title: "Research Portfolio"
output: 
  html_document:
    css: style.css
    code_folding: hide
    theme: lumen 
    toc: false
    number_sections: false
---

```{r global, include=FALSE, echo = FALSE}
### Load library ####
require(dplyr) || {install.packages("dplyr"); require(dplyr)}
require(tidyr) || {install.packages("tidyr"); require(tidyr)}
require(reshape2) || {install.packages("reshape2"); require(reshape2)}
require(ggplot2) || {install.packages("ggplot2"); require(ggplot2)}
require(doBy) || {install.packages("doBy"); require(doBy)}
require(data.table) || {install.packages("data.table"); require(data.table)}
require(tibble) || {install.packages("tibble"); require(tibble)}
require(forcats) || {install.packages("forcats"); require(forcats)}
require(gridExtra) || {install.packages("gridExtra"); require(gridExtra)}
require(RColorBrewer) || {install.packages("RColorBrewer"); require(RColorBrewer)}
require(ggrepel) || {install.packages("ggrepel"); require(ggrepel)}
require(DT) || {install.packages("DT"); require(DT)}

### Other set-up features ####
options(dplyr.summarise.inform = FALSE)

``` 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Anne Hill**  
[Linkedin](https://www.linkedin.com/in/anne-hill-411238141/)  
Email: anhill1569@gmail.com

***

**Examples of Research and Analysis Projects**

1. **Dissertation Study** 
    * [*Link to example*](https://anne2hill.github.io/DissertationExample/)  
    * This example describes one of the studies I conducted as part of my dissertation for a Ph.D. in Psychology. The document includes code excerpts in R featuring:
        * Analyses of the experimental data
        * A power analysis simulation of bootstraped data for a replication study    
  
2. **Employment Security in NYC** 
    * [*Link to example*](https://anne2hill.github.io/COVID_NYC_Example/)
    * This example provides an overview of research I conducted as part of a blog series on COVID-19's impact on New York City. The blog post is linked below, and this document provides additional details on the analysis process.
    
3. **Writing Samples:**
    * [The COVID Economy: A Difficult and Unequal Recovery](https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html) 
    
    * [COVID-19 Housing Crisis: The Worst is Yet to Come](https://medium.com/nyc-opportunity/covid-19-housing-crisis-the-worst-is-yet-to-come-47c120940dc7)

4. **Plotly Mapbox**  
    * [PPP Loan Distributions in NYC](https://prunycmapsfigures.github.io/Loan_Distribution_by_NYC_Zipcode.html) 
        * I created this map to visualize analyses conducted by Dr. Jihyun Shin as part of a blog post she wrote on the Paycheck Protection Program
    
    * [Eviction Rates across NYC](https://prunycmapsfigures.github.io/Eviction_data_by_NYC_zipcode.html) 
        * I created this map to as part of my analyses of eviction rates in NYC
    

    

